\textbf{Urban mobility in Latin America after COVID-19}

### 2024-01-22 manuscript/manuscript.qmd
update intro

Spatial human mobility is key to creating sustainable, liveable and inclusive cities.
At the societal level, spatial mobility enables the transfer of knowledge, skills and labour to places they are needed.
Spatial mobility also shapes service and transport demand across urban spaces, and enables the monitoring and control of transmissible diseases.
At the individual level, spatial mobility enables people to access and achieve opportunities and aspirations.
Understanding spatial human mobility is thus important to supporting appropriate policy responses to address societal challenges relating to carbon emissions, urban planning, service delivery, public health, disaster management and transport.

@@

A key barrier to continously monitor changes in geographic mobility patterns in less developed countries during and post the COVID-19 pandemic has been the lack of suitable data.
Traditionally census and survey data have been employed to analyse human mobility patterns in these countries.
Yet, these data streams are not frequently updated and suffer from slow releases, with census data for example
being collected over intervals of ten years in most countries.
These data streams thus lack the temporal granularity to analyse population movements over short-time periods.
Data resulting from social interactions on digital platforms has emerged as an unique source of information to capture human population movement at scale in less developed countries.
Particularly location data from mobile phone applications have become a prominent source to sense patterns of human mobility at higher geographical and temporal resolution over in real time.

@@

## The impact of COVID-19 on patterns of urban mobility

>>>>

Spatial human mobility is key to creating sustainable, liveable and inclusive cities.
At the societal level, spatial mobility enables the transfer of knowledge, skills and labour to places they are needed.
Spatial mobility also shapes service and transport demand across urban spaces, and enables the monitoring and control of transmissible diseases.
At the individual level, mobility enables people to access and achieve opportunities and aspirations in space.
Understanding spatial human mobility is thus important to supporting appropriate policy responses to address societal challenges relating to carbon emissions, urban planning, service delivery, public health, disaster management and transport.

@@

A key barrier to continuously monitor changes in geographic mobility patterns in less developed countries during and post the COVID-19 pandemic has been the lack of suitable data.
Traditionally census and survey data have been employed to analyse human mobility patterns in these countries.
Yet, these data streams are not frequently updated and suffer from slow releases, with census data for example being collected over intervals of ten years in most countries.
Traditional data streams thus lack the temporal granularity to analyse population movements over short-time periods and offer an up-to-date representation of the urban mobility system.
Data resulting from social interactions on digital platforms have emerged as an unique source of information to deliver this representation and capture human population movement in less developed countries at scale.
Particularly location data from mobile phone applications have become a prominent source to sense patterns of human mobility at higher geographical and temporal resolution in real time.

@@

## The impact of COVID-19 on urban mobility

### 2024-01-22 manuscript/manuscript.tex
update intro

\date{}
\begin{document}
\maketitle
\begin{abstract}
The COVID‐19 pandemic has impacted the national systems of population
movement around the world.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, interior hidden, sharp corners, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, frame hidden, breakable]}{\end{tcolorbox}}\fi

>>>>

\date{}
\begin{document}
\maketitle
\begin{abstract}
The COVID‐19 pandemic has impacted the national systems of population
movement around the world.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, frame hidden, interior hidden, enhanced, breakable, sharp corners, boxrule=0pt]}{\end{tcolorbox}}\fi
